{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-03-01 Paper_ttbarH_Draft.tex

%%%%%%%%%%%%%%%%% FIGURA 2 %%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\begin{figure}[th]
\centering
\includegraphics[scale=0.6]{esquematico_II.pdf}
\vspace*{0.02\textwidth}
\caption{Schematic representation of the process $g_ag_b\to t(\to
  b_i{\ell}^+\nu_{\ell})\tbar(\to \bbar_j {\ell}^- \nubar) H$. The
  indices $i,j$ denote the colour of the quarks while $a,b$ are gluon
  indices.}
\label{fig2}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To derive the above expressions, we begin by considering the
schematic representation for the process $g_ag_b\to t(\to
b_i{\ell}^+\nu_{\ell})\,\tbar(\to \bbar_j {\ell}^- \nubar)\,H$
that is sketched in Fig.~\ref{fig2}.
Here $a$ and $b$ denote the initial-state gluons and
$i$ and $j$ refer to the colours of the top and antitop quarks.
%\par
%
The amplitude for this process may be written in the following
compact form
%
\beq
\label{eq6}
\mathcal{M}^{ab,ij}=\bar{\psi}_t\,\mathcal{A}^{ab,ij}\,\psi_{\tbar}\,,
\eeq
%
where the spinors $\bar{\psi}_t$ and $\psi_{\tbar}$
contain all of the information regarding the decay of the
virtual top and anti-top, respectively,
and where the quantity $A^{ab,ij}$ is given by
%
\beq
\label{eq5}
\mathcal{A}^{ab,ij}\equiv A^{ab,ij}_{\mu\nu}(\epsilon_{\lambda_a})^{\mu}(\epsilon_{\lambda_b})^{\nu}=\sum_{k=1}^8 \mathcal{A}^{ab,ij}_k =\kp \sum_{k=1}^8 \mathcal{S}^{ab,ij}_k + i\kpt \sum_{k=1}^8 \mathcal{P}^{ab,ij}_k.
\eeq 
%
The sum over $k$ in the above expression
corresponds to the eight gluon-initiated
diagrams indicated in Fig.~\ref{fig1} {\bf (KK: correct?)}; also,
$\epsilon_{\lambda_a}$ and $\epsilon_{\lambda_b}$ are the
polarization vectors corresponding to $g_a$ and $g_b$, respectively.
In the last equality in Eq.~(\ref{eq5})
we have explicitly separated the amplitude into
two sums, with one sum corresponding to the scalar contributions
and the other to the pseudoscalar ones.
Taking all of the final-state particles to be massless, we can use the
spinor techniques
developed in \cite{Kleiss} to write $\bar{\psi}_t$ and
$\psi_{\tbar}$ as follows\footnote{These spinor techniques can also be used
  for massive final-state particles. Given the
  energy scale involved in the process in question, however, the assumption
  of massless final-state particles is sensible and greatly
  simplifies the derivation of Eq.~(\ref{eq2}).}
%
\bea
\label{eq7}
\bar{\psi}_t &=& -g^2\, \mathbb{P}_t(t)\,\mathbb{P}_W(t-b)\,
   \langle b-|\nu_{\ell}+\rangle \langle {\ell}^+\!+|(\tslash+m_t)\\
\label{eq8}
\psi_{\tbar} &=& -g^2\, \mathbb{P}_t(\tbar)\,\mathbb{P}_W(\tbar-\bbar)\,
   \langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,
\eea
%
where $|i+(-)\rangle \equiv (1/2)(1\pm \gamma^5)\,\psi_i$
represents a right-handed (left-handed) chiral spinor for final-state
particle $i$ and $\langle i+(-)|$ represents the corresponding adjoint spinor.
{\bf (KK: Do we mean the adjoint spinor, related by $C \psi^T$,
  or whatever?)}
Also, $\mathbb{P}_t(q)=(q^2-m^2_t+im_t\Gamma_t)^{-1}$ and
$\mathbb{P}_W(q)=(q^2-M^2_W+im_W\Gamma_W)^{-1}$, and
we have denoted the momenta of the various particles by the symbols
that refer to the names of those particles~\cite{Mangano}.

@@

The expression derived above for the scattering cross
section [see Eq.~(\ref{eq2}), as well as Eq.~(\ref{eq17})]
provides significant insight into
how one might analyze $\ppprocess$ in order to determine
the nature of the top-Higgs coupling.  In particular,
let us focus on the production amplitude,
$\mathcal{M}(g_ag_b \to t^i(n_t)\tbar^j(n_{\tbar})H))$, which forms
part of the overall amplitude in Eq.~(\ref{eq17}).
The absolute value squared of the production amplitude
is used to determine $d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)$,
which in turn forms part of the expression for the ``factorized'' cross section
in Eq.~(\ref{eq2}).  Summing over colour and gluon indices
we have
%
\beq
\label{eq18}
\sum_{\substack{a,b \\ i,j}}|\mathcal{M}(g_ag_b \to t^i(n_t)\tbar^j(n_{\tbar})H)|^2=\sum_{\substack{a,b \\ i,j}}\left|\sum^{8}_{k=1}C^{ab,ij}_k\,\bar{\phi}_t (\kp\mathcal{S}_k+i\kpt\mathcal{P}_k)\phi_{\tbar}\right|^2,
\eeq
%
where we have separated the colour structure of each diagram by defining
{\bf (KK: do these need $k$ subscripts?)}
$\mathcal{S}^{ab,ij}= C^{ab,ij}_k \mathcal{S}$ and
$\mathcal{P}^{ab,ij}= C^{ab,ij}_k \mathcal{P}$
[see Eqs.~(\ref{eq5}) and (\ref{eq16})]. Also, the factors
$g^2_s m_t/v$ and $-ig^2_s m_t/v$ arising from the vertices of the $t$-
and $s$-channel diagrams respectively have been included in the
definition of $C^{ab,ij}_k$ for convenience. The terms linear in $\kp$
and $\kpt$ can be written as
%
\beq
\label{eq19}
\mathcal{O}(\kp\kpt)\to \frac{1}{2}\kp\kpt \sum_{k,r}\mathbb{C}_{kr}\mathrm{Im}
\left\lbrace \mathrm{Tr}\left[ (1+\nslash_t \gamma^5)(\tslash+m_t)\mathcal{S}_k(1+\nslash_{\tbar}\gamma^5
 )(\tbslash -m_t)\tilde{\mathcal{P}}_r \right] \right\rbrace ,
\eeq
%
where the factor $\mathbb{C}_{kr}=\sum_{ab,ij}C^{ab,ij}_k
C^{ab,ij*}_r$ is real and where $\tilde{\mathcal{P}}_r = \gamma^0
\mathcal{P}_r \gamma^0$ {\bf (KK: wouldn't this be
  $\mathcal{P}_r^\dagger$? I didn't look for this in the notes
  yet, so maybe I'm just missing something)}.
The only terms that yield non-zero contributions
in the above sum are those with an
odd number of $\gamma^5$ matrices; these lead to triple-product
(TP) structures
of the form $\epsilon_{\alpha\beta\gamma\delta}\,p^{\alpha}_ap^{\beta}_bp^{\gamma}_cp^{\delta}_d$,
where $p_a$-$p_d$ represent various four momenta associated with the process.
In contrast,
it can be seen from Eq.~(\ref{eq18}) that the terms proportional to
$\kp^2$ and $\tilde{\kappa}^2_t$ descend from traces containing
an even number of $\gamma^5$
matrices and can be written in terms of scalar products of the
available momenta.\par
%\vspace*{-2mm}

With the above considerations in mind, it is useful to
write a general expression for the differential cross
section $d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)$
in terms of the momenta $q=(q_1-q_2)/2$,
$Q=(q_1+q_2)/2$, $t$, $\bar{t}$, $n_t$ and $n_{\tbar}$, where
$q_{1,2}$ denote the momenta of the initial-state gluons. Note that with this
choice, $q\cdot Q=0$ and $Q^2=-q^2=M^2_{t\tbar H}/4$, where $M_{t\tbar
  H}$ is the invariant mass of the $t\tbar H$ system.
Fifteen TPs can be constructed from these six
four-vectors,\footnote{We note that these fifteen
  TPs are not linearly independent (see the epsilon relations
  discussed in Ref.~\cite{identities}).} so that
%
\beq
\label{eq20}
d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)= \kp^2\,f_1(p_i\cdot p_j)+\tilde{\kappa}^2_t\,f_2(p_i\cdot p_j)+\kp\kpt\,\sum^{15}_{l=1}g_l(p_i\cdot p_j)\,\epsilon_l,
\eeq   
%
where
$\epsilon_l=\epsilon_{\alpha\beta\gamma\delta}\,p^{\alpha}_ap^{\beta}_bp^{\gamma}_cp^{\delta}_d$
denotes the $l$th TP (we adopt the convention $\epsilon_{0123}=+1$) and where $p_i$ and $p_j$ refer to any of the
six momenta.  The
functions $f_{1,2}$ and $g_k$ depend only on the possible scalar
products and are therefore even under a parity transformation
($\mathrm{P}$). However, the terms linear in $\kp\kpt$ are
$\mathrm{P}$-odd due to the presence of the $\mathrm{P}$-odd
TPs. Hence, only the functions $f_{1,2}$ will contribute to the total
cross-section, whereas the TP terms will be sensitive to the sign of
the anomalous coupling $\kpt$. Of the fifteen TPs mentioned above,
we will focus on those that contain both of the spin
vectors $n_t$ and $n_{\tbar}$, but do not include $q$.
The decision not to consider $q$-dependent TPs is motivated by the fact
that $q$ cannot be expressed in terms of the momenta of final state
particles (as $Q$ can, by virtue of energy-momentum conservation). The
decision to focus on TPs that contain both $n_t$ and $n_{\tbar}$
is rooted in the fact that the spins of pair-produced top and antitop quarks
are highly correlated at hadron colliders 
(even though the quarks themselves are unpolarized). {\bf (KK: did I reword
  this correctly?)}
Observables that combine the decay products of the
$t$ and $\tbar$ will be sensitive to this spin
correlation~\cite{Bernreuther}.  A similar behaviour is expected in $t\tbar H$
production, where it can be shown that single-spin asymmetries
vanish~\cite{Ellis,Biswas}. Hence, in order to construct observables
sensitive to the structure of the $tH$ coupling, we will restrict our attention
to those
TPs that include information on the decay products of both the top and
anti-top quarks. Only five of the fifteen TPs in Eq.~(\ref{eq20}) do
not involve the four vector $q$ and, among these, only three
include both $n_t$ and $n_{\tbar}\,$.  Thus, we will restrict our attention
to the following TPs
%
\beq
\label{eqa1}
\epsilon_1\equiv\epsilon(t,\tbar,n_t,n_{\tbar}),\,\,
\vspace*{1mm}
\eeq
%
\beq
\label{eqa2}
\epsilon_2\equiv\epsilon(Q,\tbar,n_t,n_{\tbar}),
\vspace*{1mm}
\eeq
%
\beq
\label{eqa3}
\epsilon_3\equiv\epsilon(Q,t,n_t,n_{\tbar}).
\vspace*{1mm}
\eeq
%
\par

Before turning to a consideration of various CP-odd observables,
we remark that even though all of the above discussion took place
within the context of $gg$-initiated production, similar conclusions
are obtained for $q\qbar$-initiated production. In particular, the
definitions of the spin vectors in Eqs.~(\ref{eq3})-(\ref{eq4}) and
the general form of $d\sigma$ introduced in Eq.~(\ref{eq20}) are valid
in both cases.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setlength{\belowdisplayskip}{10pt} \setlength{\belowdisplayshortskip}{10pt}
%\setlength{\abovedisplayskip}{10pt} \setlength{\abovedisplayshortskip}{10pt}
\bigskip
\section{$\mathrm{\mathbf{CP}}$-odd observables}
\label{sec3}
In this section we present three types of observables based on the TPs discussed
in Sec.~\ref{sec2}, namely, asymmetries, angular
distributions and mean values. These observables are sensitive not only to the
magnitude of the pseudoscalar coupling $\kpt$, but also to its
sign.  In order to test the various observables, we have
used $\mathtt{MadGraph5\_aMC@NLO}$ \cite{Madgraph} to simulate the process
$\ppprocess$ at parton level for different values of the couplings
$\kp$ and $\kpt$.  In all cases we have generated $10^5$ events
and have assumed a center-of-mass energy of
$14\,\mathrm{TeV}$.\footnote{Note that, since we generate
  the same number of events in
  each case, the corresponding integrated luminosities are different, since the
  cross section depends on the value of $\kpt$.}
We have also imposed the
following set of cuts: $p_T$ of leptons $> 10\,\mathrm{GeV}$, $|\eta|$
of leptons $< 2.5$, $|\eta|$ of b jets $< 2.5$ and $\Delta
R_{\ell\ell}>0.4$.  Note that we have used this
somewhat large number of events ($10^5$) in order to determine clearly
the extent to which the proposed observables are sensitive to the NP
coupling.  Section~\ref{sec6} contains an
analysis of the experimental feasibility of the more promising observables.
{\bf (KK: I may not have worded this quite correctly.)}

Before continuing on to our analysis, let us make a few comments
regarding the values that we choose for $\kp$ and $\kpt$.
First of all, we note that if the pseudoscalar
coupling $\kpt$ is the only source of physics beyond the SM,
then indirect contraints (based on Higgs production via gluon fusion,
followed by Higgs decay to two photons {\bf (KK: can we just say
  something like $gg\to H \to \gamma\gamma$?  Or is that not
  correct?)}) disfavour $\kp < 0$ but do not
resolve the degeneracy {\bf (KK: did I reword this correctly?)}
in the sign of $\kpt$ \cite{Guadagnoli}. On
the other hand, if one assumes that the tensor structure of the
Higgs interactions are the
same as those of the SM and if one parameterizes these interactions via
one universal Higgs coupling to vector bosons, $\kappa_V$, and one
universal Higgs coupling to fermions, $\kappa_f$, then the measured signal
strengths provided by the ATLAS and CMS collaborations are compatible with
the values predicted by the SM, (namely, $\kappa_f=1$ and $\kappa_V=1$).
With these facts in mind, we will, for the most part,
set the value of the scalar coupling to its SM
value ($\kp=1$) and will allow the pseudoscalar coupling to take on
various values (including both possible signs). In particular, we
analyze the cases $\kpt=0,\pm 0.25, \pm 0.5, \pm 0.75,\pm 1$.
In addition, we also provide some analysis regarding the pure
$\mathrm{CP}$-odd case ($\kp=0,\kpt=1$).
%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymmetry}
%\bigskip
\label{sec3.1}

@@

the numerators of the {\bf (KK: did I reword this correctly?)}

@@

$\kp$ and $\kpt$, they expected to vanish in these cases. However, we
will show in the next section {\bf (KK: subsection?)}

>>>>

%%%%%%%%%%%%%%%%% FIGURA 2 %%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{esquematico_II.pdf}
\vspace*{0.02\textwidth}
\caption{Schematic representation of the process $g_ag_b\to t(\to
  b_i{\ell}^+\nu_{\ell})\tbar(\to \bbar_j {\ell}^- \nubar) H$. The
  indices $i,j$ denote the colour of the quarks while $a,b$ are gluon
  indices.}
\label{fig2}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To derive the above expressions, we begin by considering the
schematic representation for the process $g_ag_b\to t(\to
b_i{\ell}^+\nu_{\ell})\,\tbar(\to \bbar_j {\ell}^- \nubar)\,H$
that is sketched in Fig.~\ref{fig2}.
Here $a$ and $b$ denote the initial-state gluons and
$i$ and $j$ refer to the colours of the top and antitop quarks.
%\par
%
The amplitude for this process may be written in the following
compact form
%
\beq
\label{eq6}
\mathcal{M}^{ab,ij}=\bar{\psi}_t\,\mathcal{A}^{ab,ij}\,\psi_{\tbar}\,,
\eeq
%
where the spinors $\bar{\psi}_t$ and $\psi_{\tbar}$
contain all of the information regarding the decay of the
virtual top and anti-top, respectively,
and where the quantity $A^{ab,ij}$ is given by
%
\beq
\label{eq5}
\mathcal{A}^{ab,ij}\equiv A^{ab,ij}_{\mu\nu}(\epsilon_{\lambda_a})^{\mu}(\epsilon_{\lambda_b})^{\nu}=\sum_{k=1}^8 \mathcal{A}^{ab,ij}_k =\kp \sum_{k=1}^8 \mathcal{S}^{ab,ij}_k + i\kpt \sum_{k=1}^8 \mathcal{P}^{ab,ij}_k.
\eeq 
%
The sum over $k$ in the above expression
corresponds to the eight gluon-initiated
diagrams indicated in Fig.~\ref{fig1}; also,
$\epsilon_{\lambda_a}$ and $\epsilon_{\lambda_b}$ are the
polarization vectors corresponding to $g_a$ and $g_b$, respectively.
In the last equality in Eq.~(\ref{eq5})
we have explicitly separated the amplitude into
two sums, with one sum corresponding to the scalar contributions
and the other to the pseudoscalar ones.
Taking all of the final-state particles to be massless, we can use the
spinor techniques
developed in \cite{Kleiss} to write $\bar{\psi}_t$ and
$\psi_{\tbar}$ as follows\footnote{These spinor techniques can also be used
  for massive final-state particles. Given the
  energy scale involved in the process in question, however, the assumption
  of massless final-state particles is sensible and greatly
  simplifies the derivation of Eq.~(\ref{eq2}).}
%
\bea
\label{eq7}
\bar{\psi}_t &=& -g^2\, \mathbb{P}_t(t)\,\mathbb{P}_W(t-b)\,
   \langle b-|\nu_{\ell}+\rangle \langle {\ell}^+\!+|(\tslash+m_t)\\
\label{eq8}
\psi_{\tbar} &=& g^2\, \mathbb{P}_t(\tbar)\,\mathbb{P}_W(\tbar-\bbar)\,
   \langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,
\eea
%
where $|i+(-)\rangle \equiv (1/2)(1\pm \gamma^5)\,\psi_i$
represents a right-handed (left-handed) chiral spinor for final-state
particle $i$ and $\langle i+(-)|$ represents the corresponding adjoint spinor.
{\bf (KK: Do we mean the adjoint spinor, related by $C \psi^T$,
  or whatever?, N: It is $\psi^{\dagger}\gamma^0$. I'm using the name given in Eq(2.28) of Bjorken and Drell's book.)}
Also, $\mathbb{P}_t(q)=(q^2-m^2_t+im_t\Gamma_t)^{-1}$ and
$\mathbb{P}_W(q)=(q^2-m^2_W+im_W\Gamma_W)^{-1}$, and
we have denoted the momenta of the various particles by the symbols
that refer to the names of those particles~\cite{Mangano}.

@@

The expression derived above for the scattering cross
section [see Eq.~(\ref{eq2}), as well as Eq.~(\ref{eq17})]
provides significant insight into
how one might analyze $\ppprocess$ in order to determine
the nature of the top-Higgs coupling.  In particular,
let us focus on the production amplitude,
$\mathcal{M}(g_ag_b \to t^i(n_t)\tbar^j(n_{\tbar})H))$, which forms
part of the overall amplitude in Eq.~(\ref{eq17}).
The absolute value squared of the production amplitude
is used to determine $d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)$,
which in turn forms part of the expression for the ``factorized'' cross section
in Eq.~(\ref{eq2}).  Summing over colour and gluon indices
we have
%
\beq
\label{eq18}
\sum_{\substack{a,b \\ i,j}}|\mathcal{M}(g_ag_b \to t^i(n_t)\tbar^j(n_{\tbar})H)|^2=\sum_{\substack{a,b \\ i,j}}\left|\sum^{8}_{k=1}C^{ab,ij}_k\,\bar{\phi}_t (\kp\mathcal{S}_k+i\kpt\mathcal{P}_k)\phi_{\tbar}\right|^2,
\eeq
%
where we have separated the colour structure of each diagram by defining
$\mathcal{S}^{\,ab,ij}_k= C^{ab,ij}_k \mathcal{S}_k$ and
$\mathcal{P}^{\,ab,ij}_k= C^{ab,ij}_k \mathcal{P}_k$
[see Eqs.~(\ref{eq5}) and (\ref{eq16})]. Also, the factors
$g^2_s m_t/v$ and $-ig^2_s m_t/v$ arising from the vertices of the $t$-
and $s$-channel diagrams respectively have been included in the
definition of $C^{ab,ij}_k$ for convenience. The terms linear in $\kp$
and $\kpt$ can be written as
%
\beq
\label{eq19}
\mathcal{O}(\kp\kpt)\to \frac{1}{2}\kp\kpt \sum_{k,r}\mathbb{C}_{kr}\mathrm{Im}
\left\lbrace \mathrm{Tr}\left[ (1+\nslash_t \gamma^5)(\tslash+m_t)\mathcal{S}_k(1+\nslash_{\tbar}\gamma^5
 )(\tbslash -m_t)\tilde{\mathcal{P}}_r \right] \right\rbrace ,
\eeq
%
where the factor $\mathbb{C}_{kr}=\sum_{ab,ij}C^{ab,ij}_k
C^{ab,ij*}_r$ is real and where $\tilde{\mathcal{P}}_r = \gamma^0
\mathcal{P}^{\dagger}_r \gamma^0$.
The only terms that yield non-zero contributions
in the above sum are those with an
odd number of $\gamma^5$ matrices; these lead to triple-product
(TP) structures
of the form $\epsilon_{\alpha\beta\gamma\delta}\,p^{\alpha}_ap^{\beta}_bp^{\gamma}_cp^{\delta}_d$,
where $p_a$-$p_d$ represent various four momenta associated with the process.
In contrast,
it can be seen from Eq.~(\ref{eq18}) that the terms proportional to
$\kp^2$ and $\tilde{\kappa}^2_t$ descend from traces containing
an even number of $\gamma^5$
matrices and can be written in terms of scalar products of the
available momenta.\par
%\vspace*{-2mm}

With the above considerations in mind, it is useful to
write a general expression for the differential cross
section $d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)$
in terms of the momenta $q=(q_1-q_2)/2$,
$Q=(q_1+q_2)/2$, $t$, $\bar{t}$, $n_t$ and $n_{\tbar}$, where
$q_{1,2}$ denote the momenta of the initial-state gluons. Note that with this
choice, $q\cdot Q=0$ and $Q^2=-q^2=M^2_{t\tbar H}/4$, where $M_{t\tbar
  H}$ is the invariant mass of the $t\tbar H$ system.
Fifteen TPs can be constructed from these six
four-vectors,\footnote{We note that these fifteen
  TPs are not linearly independent (see the epsilon relations
  discussed in Ref.~\cite{identities}).} so that
%
\beq
\label{eq20}
d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)= \kp^2\,f_1(p_i\cdot p_j)+\tilde{\kappa}^2_t\,f_2(p_i\cdot p_j)+\kp\kpt\,\sum^{15}_{l=1}g_l(p_i\cdot p_j)\,\epsilon_l,
\eeq   
%
where
$\epsilon_l=\epsilon_{\alpha\beta\gamma\delta}\,p^{\alpha}_ap^{\beta}_bp^{\gamma}_cp^{\delta}_d$
denotes the $l$th TP (we adopt the convention $\epsilon_{0123}=+1$) and where $p_i$ and $p_j$ refer to any of the
six momenta.  The
functions $f_{1,2}$ and $g_k$ depend only on the possible scalar
products and are therefore even under a parity transformation
($\mathrm{P}$). However, the terms linear in $\kp\kpt$ are
$\mathrm{P}$-odd due to the presence of the $\mathrm{P}$-odd
TPs. Hence, only the functions $f_{1,2}$ will contribute to the total
cross-section, whereas the TP terms will be sensitive to the sign of
the anomalous coupling $\kpt$. Of the fifteen TPs mentioned above,
we will focus on those that contain both of the spin
vectors $n_t$ and $n_{\tbar}$, but do not include $q$.
The decision not to consider $q$-dependent TPs is motivated by the fact
that $q$ cannot be expressed in terms of the momenta of final state
particles (as $Q$ can, by virtue of energy-momentum conservation). The
decision to focus on TPs that contain both $n_t$ and $n_{\tbar}$
is rooted in the fact that the spins of pair-produced top and antitop quarks
are highly correlated at hadron colliders 
(even though the quarks themselves are unpolarized).
Observables that combine the decay products of the
$t$ and $\tbar$ will be sensitive to this spin
correlation~\cite{Bernreuther}.  A similar behaviour is expected in $t\tbar H$
production, where it can be shown that single-spin asymmetries
vanish~\cite{Ellis,Biswas}. Hence, in order to construct observables
sensitive to the structure of the $tH$ coupling, we will restrict our attention
to those
TPs that include information on the decay products of both the top and
anti-top quarks. Only five of the fifteen TPs in Eq.~(\ref{eq20}) do
not involve the four vector $q$ and, among these, only three
include both $n_t$ and $n_{\tbar}\,$.  Thus, we will restrict our attention
to the following TPs
%
\beq
\label{eqa1}
\epsilon_1\equiv\epsilon(t,\tbar,n_t,n_{\tbar}),\,\,
\vspace*{1mm}
\eeq
%
\beq
\label{eqa2}
\epsilon_2\equiv\epsilon(Q,\tbar,n_t,n_{\tbar}),
\vspace*{1mm}
\eeq
%
\beq
\label{eqa3}
\epsilon_3\equiv\epsilon(Q,t,n_t,n_{\tbar}).
\vspace*{1mm}
\eeq
%
\par

Before turning to a consideration of various CP-odd observables,
we remark that even though all of the above discussion took place
within the context of $gg$-initiated production, similar conclusions
are obtained for $q\qbar$-initiated production. In particular, the
definitions of the spin vectors in Eqs.~(\ref{eq3})-(\ref{eq4}) and
the general form of $d\sigma$ introduced in Eq.~(\ref{eq20}) are valid
in both cases.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setlength{\belowdisplayskip}{10pt} \setlength{\belowdisplayshortskip}{10pt}
%\setlength{\abovedisplayskip}{10pt} \setlength{\abovedisplayshortskip}{10pt}
\bigskip
\section{$\mathrm{\mathbf{CP}}$-odd observables}
\label{sec3}
In this section we present three types of observables based on the TPs discussed
in Sec.~\ref{sec2}, namely, asymmetries, angular
distributions and mean values. These observables are sensitive not only to the
magnitude of the pseudoscalar coupling $\kpt$, but also to its
sign.  In order to test the various observables, we have
used $\mathtt{MadGraph5\_aMC@NLO}$ \cite{Madgraph} to simulate the process
$\ppprocess$ at parton level for different values of the couplings
$\kp$ and $\kpt$.  In all cases we have generated $10^5$ events
and have assumed a center-of-mass energy of
$14\,\mathrm{TeV}$.\footnote{Note that, since we generate
  the same number of events in
  each case, the corresponding integrated luminosities are different, since the
  cross section depends on the value of $\kpt$.}
We have also imposed the
following set of cuts: $p_T$ of leptons $> 10\,\mathrm{GeV}$, $|\eta|$
of leptons $< 2.5$, $|\eta|$ of b jets $< 2.5$ and $\Delta
R_{\ell\ell}>0.4$.  Note that we have used this
somewhat large number of events ($10^5$) in order to determine clearly
the extent to which the proposed observables are sensitive to the NP
coupling.  Section~\ref{sec6} contains an
analysis of the experimental feasibility of the more promising observables.

Before continuing on to our analysis, let us make a few comments
regarding the values that we choose for $\kp$ and $\kpt$.
First of all, we note that if the pseudoscalar
coupling $\kpt$ is the only source of physics beyond the SM,
then indirect contraints (based on Higgs production via gluon fusion,
followed by Higgs decay to two photons {\bf (KK: can we just say
  something like $gg\to H \to \gamma\gamma$?  Or is that not
  correct?)}) disfavour $\kp < 0$ but do not
resolve the degeneracy in the sign of $\kpt$ \cite{Guadagnoli}. On
the other hand, if one assumes that the tensor structure of the
Higgs interactions are the
same as those of the SM and if one parameterizes these interactions via
one universal Higgs coupling to vector bosons, $\kappa_V$, and one
universal Higgs coupling to fermions, $\kappa_f$, then the measured signal
strengths provided by the ATLAS and CMS collaborations are compatible with
the values predicted by the SM, (namely, $\kappa_f=1$ and $\kappa_V=1$).
With these facts in mind, we will, for the most part,
set the value of the scalar coupling to its SM
value ($\kp=1$) and will allow the pseudoscalar coupling to take on
various values (including both possible signs). In particular, we
analyze the cases $\kpt=0,\pm 0.25, \pm 0.5, \pm 0.75,\pm 1$.
In addition, we also provide some analysis regarding the pure
$\mathrm{CP}$-odd case ($\kp=0,\kpt=1$).
%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymmetry}
%\bigskip
\label{sec3.1}

@@

the numerators of the 

@@

$\kp$ and $\kpt$, they {\bf are} expected to vanish in these cases. However, we
will show in the next subsection
